xwMOOC 딥러닝

### 2018-09-26 r-keras-fashion-mnist.Rmd
added fashion mnist kaggle data

par(mfcol=c(5,5))
par(mar=c(0, 0, 1.5, 0), xaxs='i', yaxs='i')
for (i in 1:25) { 
  img <- train_images[i, , ]
  img <- t(apply(img, 2, rev))
  image(1:28, 1:28, img, col = gray((0:255)/255), xaxt = 'n', yaxt = 'n',
        main = paste(class_names[train_labels[i] + 1]))
}
```

>>>>

display_fashion <- function(input, i){
  m <- matrix(unlist(input), nrow = 28, byrow = FALSE)
  # m <- t(apply(apply(m, 2, rev),2, rev))
  # m <- t(apply(m, 2, rev))
  m <- t(apply(t(m), 2, rev))
  image(m, col=grey.colors(255),  xaxt = 'n', yaxt = 'n',
        main = paste(class_names[train_labels[i] + 1]))
}

par(mfrow = c(3,5))
map(sample(1:nrow(train_images), 15), ~display_fashion(train_images[.x,], .x))
```
